Staged Abstract Interpreters

### 2019-08-31 paper/70_eval.tex
tweak for latexdiff
misc update

We use Scala 2.12.8 and Oracle JVM 1.8.0-191 \footnote{The options for
running JVM is set to the following: \texttt{-Xms2G -Xmx8G -Xss1024M
-XX:MaxMetaspaceSize=2G - XX:ReservedCodeCacheSize=2048M}},
running on an Ubuntu 16.04 LTS (kernel 4.4.0) machine. All of our
evaluations were performed on a machine with 4 Intel Xeon Platinum
8168 CPU at 2.7GHz and 3 TiB of RAM. Although the machine has 96 cores
(192 threads) in total, the abstract interpreters are single-threaded.
To minimize the effect of warming-up from the HotSpot JIT compiler,
all the experiments are executed for 20 times and we report the
statistical median value of the running times. We set a 5 minutes
timeout.

@@

Figure~\ref{evaluation_result} shows the evaluation result, comparing the
performance improved by staging on the two monovariant CFAs The
\textit{unstaged} and \textit{staged} columns show the median time to finish
the analysis. The column $\frac{\text{unstaged}}{\text{staged}}$ shows the
improvement. The dash - in some cells indicates timeout.  As
expected, the staged version significantly outperforms the unstaged version on
all benchmarks. We observe that simple and homogeneous domain used in the
benchmark usualy leads to better speed-ups.  For 0CFA w/o store-widening, we
observe an average speed-up of ~17x times; for 0CFA w/ store-widening, the
average speed-up is ~7x times.  The @kcfa-worst-64@ benchmark has the most
speed-up among all the tests. Although it has a comparablely large size of AST,
it has a quite simple structure which only involves booleans, functions and
applications. We conjecture that the simple domain and structure allow the
generated code to be efficiently optimized by the JVM. But on the corresponding
0CFA-SW, we do not observe such great speed-up. Due to the complexity of
generated code and next-stage running platform (JVM), we leave the detailed
empirical analysis of which static analysis can benefit more from
specialization as future work.

>>>>

We use Scala 2.12.8 and Oracle JVM 1.8.0-191 \footnote{The options for
running JVM is set to the following: \texttt{-Xms2G -Xmx8G -Xss1024M
-XX:MaxMetaspaceSize=2G - XX:ReservedCodeCacheSize=2048M}},
running on an Ubuntu 16.04 LTS (kernel 4.4.0) machine. All of our
evaluations were performed on a machine with 4 Intel Xeon Platinum
8168 CPU at 2.7GHz and 3 TiB of RAM. Although the machine has 96 cores
(192 threads) in total, the abstract interpreters are single-threaded.
To minimize the effect of warm-up from the HotSpot JIT compiler,
all the experiments are executed for 20 times and we report the
statistical median value of the running times. We set a 5 minutes
timeout.

@@

Figure~\ref{evaluation_result} shows the evaluation result, comparing the
performance improved by staging on the two monovariant CFAs The
\textit{unstaged} and \textit{staged} columns show the median time to finish
the analysis. The column $\frac{\text{unstaged}}{\text{staged}}$ shows the
improvement. The dash - in some cells indicates timeout.  As
expected, the staged version significantly outperforms the unstaged version on
all benchmarks. We observe that simple and homogeneous value domains used in the
benchmark usually leads to better speed-ups.  For 0CFA w/o store-widening, we
observe an average speed-up of ~17x times; for 0CFA w/ store-widening, the
average speed-up is ~7x times.  The \texttt{kcfa-worst-64} benchmark has the most
speed-up among all the tests. Although it has a comparablely large size of AST,
it has a quite simple structure which only involves booleans, functions and
applications. We conjecture that the simple domain and structure allow the
generated code to be efficiently optimized by the JVM. But on the corresponding
0CFA-SW, we do not observe such great speed-up. Due to the complexity of
generated code and next-stage running platform (JVM), we leave the detailed
empirical analysis of which static analysis can benefit more from
specialization as future work.
